\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-10 manuscript.Rmd
Knitable Script (dependency problem yet to solve)

```{r setup, include = FALSE}
library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(correlation)
library(ggcorrplot)
library(car) #Reversecoding
library(Hmisc)
library(semTable)
r_refs("references.bib")
```

@@

```{r factor_identification_fig, out.height= "50%",  fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method', fig.show="hold",fig.ncol = 2, out.width="50%",  warning=FALSE}
knitr::include_graphics('parallel.png')
scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
      hline=NULL,add=F)
knitr::include_graphics('HUll method.jpeg')

@@

```{r EFAplot,  fig.cap='Five Factor Solution', fig.align='center', out.width= "120%", out.height= "100%", warning=FALSE}
knitr::include_graphics('EFAplot.LR.png')

@@

```{r IRT data, include=FALSE}

@@

"F1 =~ item16 + item36 + item17
                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
                 F3 =~  item27+ item3+ item40 + item30 + item41
                 F4 =~ a1*item32 +item35 + item38+ a2*item33 
                 F5 =~ item46+ item45+ item25+ item4+ item1

IRTRitem8 = recode(IRT.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')

IRT.data <- IRT.data %>% 
  mutate(Ritem8 = IRTRitem8, Ritem37 = IRTRitem37)
```

>>>>

```{r setup, include = FALSE}
library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(correlation)
library(ggcorrplot)
library(car) #Reversecoding
library(Hmisc)
library(semTable)

r_refs("references.bib")
```

@@

```{r factor_identification_fig, eval=FALSE, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, fig.ncol=2, warning=FALSE, (C) Hull method', fig.show="hold", include=FALSE, out.height="50%", out.width="50%"}
knitr::include_graphics('parallel.png')
scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
      hline=NULL,add=F)
knitr::include_graphics('HUll method.jpeg')

@@

```{r EFAplot, eval=FALSE, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, include=FALSE, out.height="100%", out.width="120%"}
knitr::include_graphics('EFAplot.LR.png')

@@

```{r IRT data, eval=FALSE, include=FALSE}

@@
